---
title: "How to prepare"
author: "Gerko Vink"
date: "Statistical Programming with R"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

Dear all, 

This Spring you will participate in the **Introduction to statistical analyses with R and RStudio** course in Utrecht, the Netherlands. To realize a steeper learning curve, we will use some functionality that is not part of the base installation for `R`. The below steps guide you through installing both `R` as well as the necessary additions. 

I look forward to see you all,  

[*Gerko Vink*](https://www.gerkovink.com)

---

#### Steps to prepare:

---

1. **Install `R`**

`R` can be obtained [here](https://cran.r-project.org). We won't use `R` directly in the course, but rather call `R` through `RStudio`. Therefore it needs to be installed. 

---

2. **Install `RStudio` Desktop**

Rstudio is an Integrated Development Environment (IDE). It can be obtained as stand-alone software [here](https://www.rstudio.com/products/RStudio/), but is also available through [MyWorkplace](https://myworkplace.uu.nl/vpn/index.html).

---

3. **Install package `mice`. **

Go to `Tools` > `Install Packages` in `RStudio`. Make sure that you are connected to the internet and select  `Repository` under `Install From` and type `mice` under `Packages`. Leave the `Install to Library` at default and verify that `Install Dependencies` is selected. Click install. 

Some packages depend on other packages, meaning that their functionality may be limited if their dependencies are not installed. Installing dependencies is therefore recommended. 

If all is right, you will receive a message in the console that the package has been installed (with its dependencies). 

Alternatively, if you know the name of the package you would like to install - in this case `mice` - you can also call `install.packages("mice")` in the console window.

---

4. **Install packages dplyr, magrittr and ggplot2.**

```{r eval=FALSE}
install.packages("dplyr")
install.packages("magrittr")
install.packages("ggplot2")
```

---


